Contextual Combinatorial Cascading Bandits

### 2015-12-21 contextual combinatorial cascading bandits.tex
update format
add one part of related work

\section{Related Works}

@@

\begin{algorithm} %C^3-UCB algorithm
	\caption{C$^3$-UCB}
	\label{alg:ConComCascade}
	\begin{algorithmic}[1]
		\STATE {//Initialization}
		\STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
		\STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
		\STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}
		%\STATE{}

		\FORALL {$t=1,2,\ldots$}
			\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
			%\STATE{}

			\STATE {//Compute UCBs}
			\STATE {$\forall a\in E: $}
			\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
			%\STATE {}

			\STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
			\STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
			\STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
			\STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
			%\STATE {}

>>>>

\section{Related Work}

Our work generalizes both the cascading bandits of \cite{kveton2015cascading} and combinatorial cascading bandits of \cite{kveton2015combinatorial} to involve contextual information and position discount.
In cascading bandits of \cite{kveton2015cascading}, the feasible set contains any list of $K$ items out of $L$ ground items.
Our work generalizes the feasible set to be any set of lists of at most $K$ items, like \cite{kveton2015combinatorial}.
In both \cite{kveton2015cascading} and \cite{kveton2015combinatorial}, even though they define the feasible actions as lists, they regard them as sets. The order of a feasible action does not affect the regret bound, which might have problem in real application, especially for recommendations.

In \cite{kveton2015cascading}, they found that recommending items in chosen action in increasing order of their UCBs has better performance than in decreasing order of their UCBs.
This result might conflict with recommendations in real world.
To improve the quality of user experience, we usually list items with higher preference first and then lower preference items.
Our work extends this part by introducing position discounted parameters.
Under our setting, the items with higher preference will come first.

@@

\begin{algorithm} %C^3-UCB algorithm
  \caption{C$^3$-UCB}
  \label{alg:ConComCascade}
  \begin{algorithmic}[1]
    \STATE {//Initialization}
    \STATE {Parameters: $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$}
    \STATE {Parameters: $\delta > 0, \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
    \STATE {$\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}

    \FORALL {$t=1,2,\ldots$}
      \STATE {Obtain context $x_{t,a}$ for all $a\in E$}
      \STATE {//Compute UCBs}
      \STATE {$\forall a\in E: $}
      \STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \bbeta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}

      \STATE {//Choose action $\bA_t$ using UCBs $\bU_t$}
      \STATE { $\bA_t=(\ba_1^t,...,\ba_{\abs{\bA_t}}^t) \leftarrow \argmax_{A \in \cS} f(A, \bU_t)$ } 
      \STATE {//In the conjunctive case, use $f_{\wedge}$ in stead of $f$}
      \STATE {Play $\bA_t$ and observe $\bO_t, \bw_t(\ba_k^t), k\in[\bO_t]$}
